%!TEX root = ../../../FYP_Dissertation.tex

This module is a simple command line interface to the built-in
low-overhead profiler of LuaJIT. The lower-level API of the profiler
is accessible via the "jit.profile" module or the luaJIT\_profile\_* C API.

Example usage:
\begin{lstlisting}
  mad -jp myapp.mad
  mad -jp=s myapp.mad
  mad -jp=-s myapp.mad
  mad -jp=vl myapp.mad
  mad -jp=G,profile.txt myapp.mad
\end{lstlisting}
The following dump features are available:
 \begin{itemize}%[label={--}]
  \item \textbf{f} - Shows function name (Default mode).
  \item \textbf{F} - Shows function name with module prepend.
  \item \textbf{l} - Shows line granularity ('module':'line').
  \item \textbf{\textless number\textgreater} - Stack dump depth (callee\textless caller - Default: 1)
  \item \textbf{-\textless number\textgreater} - Inverse stack dump depth (caller\textgreater callee).
  \item \textbf{s} - Split stack dump after first stack level. Implies $\mid depth\mid$
  \textgreater= 2.
  \item \textbf{p} - Show full path for module names.
  \item \textbf{v} - Show VM states (See bellow).
  \item \textbf{z} - Show zones (See bellow).
  \item \textbf{r} - Show raw sample counts (Default: percentages).
  \item \textbf{a} - Annotate excerpts from source code files.
  \item \textbf{A} - Annotate complete source code files.
  \item \textbf{G} - Produce raw output suitable for graphical tools (See bellow).
  \item \textbf{m\textless number\textgreater} - Minimum sample percentage to be shown (Default: 3).
  \item \textbf{i\textless number\textgreater} - Sampling interval in milliseconds (Default: 10).
 \end{itemize}

 Many of those options can be activated at ones.\\

We can also use this module programmatically like in the example below. The
\emph{start} function can take 2 arguments, the list of options (describe above)
and the output file.
\begin{lstlisting}[style=LuaStyle]
local prof = require"jit.p"
prof.start("vf", "file.txt")
  -- Code to analyze here
prof.stop()
\end{lstlisting}

\paratitle{VM states:}\\
This option allows to shows the time spent in which state of the VM.
States can be of the following types :

\{Compiled - Interpreted - C code - Garbage Collector - JIT Compiler\} \\

\paratitle{Zone:}\\
Statistics can be grouped in user defined zone. Below is an example a such a
definition.
\begin{lstlisting}
    local zone = require("jit.zone")
    zone("MyZone")
      -- Lua code here
    zone()
\end{lstlisting}

\paratitle{Graphical tools:}\\
This option can be used to graphically show the dump in a nice image format
(see Appendix \ref{Apendix:fl})